---
title: "Simple document"
author: Brennan Baker
date: 9/11/2018
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r sample_chunk}
samp = rnorm(100)
length(samp)
```

ctrl+alt+i adds a new code chunk

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.
Do this for summary statistics
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Section 3: Learning assessment

Write a named code chunk that creates a variable containing a sample of size 500 from a random normal variable, computes the absolute value of each element, and produces a histogram of the result. Add an inline summary giving the median value rounded to two decimal places. What happens if you set eval = FALSE to the code chunk? What about  echo = FALSE?


```{r, include = FALSE}
library(tidyverse)
```


```{r}
plot = tibble(
  sample = rnorm(500),
  abs_sample = abs(sample)
)
ggplot(plot, aes(x = abs_sample)) + geom_histogram()
```


Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell
